Manuscript Figures for Genome Biology

### 2018-09-11 manuscript_figures/manuscript_figures.Rmd
Explicitly save alternate combined version of Fig S4; make legend labels more clear

Fig_impactofinfcov <- ggplot(dftab, aes(x = dataset, y = method, fill = diff_inf_ratio)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(topR), "", #adaptive text lab color
                                     ifelse(topR > 1, signif(topR,2), ""))), 
                  color = "white", size = 2) +
        geom_text(aes(label = ifelse(is.na(topR), "", 
                                     ifelse(topR <= 1, signif(topR,2), ""))), 
                  color = "black", size = 2)+
        scale_fill_gradientn("Fold Change\n(log2)",
                             colors = c("darkblue","white","darkred"), 
                             limits = c(-0.5, topRange), 
                             values = scales::rescale(c(-0.5, 0, topRange))) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        facet_grid( ~ casestudy + cov, scales = "free", space = "free") +
        ggtitle("Impact of informative covariate on number of rejections") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.99, 0.95), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7, angle=45, margin = margin(t=0)),
              legend.title = element_text(size = 9, margin=margin(t=-10)),
              legend.margin = margin(t=2, r=10, b=-2, l=10))

Fig_impactofinfcov
ggsave(file.path(outdir, "Figure_impactofinfcov_fc.pdf"), width = 15.5, height = 4.25)

@@

dftab <- left_join(dftab, maxVals, by = c("casestudy")) %>%
  mutate(top = ifelse(diff_inf_percent == top, diff_inf_percent, NA)) %>%
  mutate(topR = ifelse(diff_inf_ratio == topR, diff_inf_ratio, NA)) %>%
  ungroup() %>%
  mutate(casestudy = factor(casestudy, levels = colOrder)) %>%
  mutate(casestudyN = paste0(casestudy, "(", maxd, ")")) %>%
  mutate(casestudyN = factor(casestudyN, 
                             levels = unique(casestudyN)[unique(as.numeric(casestudy))]))

@@

Fig_impactofinfcov <- ggplot(dftab, aes(x = casestudy, y = method, fill = diff_inf_ratio)) + 
        geom_tile() + 
        scale_fill_gradientn("Fold Change\n(log2)",
                             colors = c("darkblue","white","darkred"), 
                             limits = c(-0.5, topRange), 
                             values = scales::rescale(c(-0.5, 0, topRange))) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        ggtitle("Impact of informative covariate") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
        geom_text(aes(label = ifelse(is.na(topR), "", #adaptive text lab color
                                     ifelse(topR > 1, signif(topR, 2), ""))), 
                  color = "white", size = 2) +
        geom_text(aes(label = ifelse(is.na(topR), "", 
                                     ifelse(topR <= 1, signif(topR, 2), ""))), 
                  color = "black", size = 2)  +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.945, 0.94), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7, angle=45, margin = margin(t=2)),
              legend.title = element_text(size = 9, margin=margin(t=-10)),
              legend.margin = margin(t=2, r=10, b=-6, l=10))

Fig_impactofinfcov
ggsave(file.path(outdir, "Figure_impactofinfcov_avg_fc.pdf"), width = 5, height = 4)

@@

pfdr <- ggplot(dftab, aes(x = size, y = method, fill = fdr_diff)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(top_fdr), "",  scales::percent(top_fdr))), 
                  color = "black", size = 2) +
        scale_fill_gradientn("% Change\nin FDR",
                             labels = scales::percent, 
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.01,0,.01)),
                             guide = "colorbar", oob=scales::squish,
                             limits=c(-.01,0.01)) +
        xlab("") + ylab("") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1))

ptpr <- ggplot(dftab, aes(x = size, y = method, fill = tpr_diff)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(top_tpr), "",  scales::percent(top_tpr))), 
                  color = "black", size = 2) +
        scale_fill_gradientn("% Change\nin TPR",
                             labels = scales::percent, 
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.01,0,.1)),
                             guide = "colorbar", oob=scales::squish,
                             limits=c(-.01,0.1)) +
        xlab("") + ylab("") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1))

@@

>>>>

Fig_impactofinfcov_fc <- ggplot(dftab, aes(x = dataset, y = method, fill = diff_inf_ratio)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(topR), "", #adaptive text lab color
                                     ifelse(topR > 1, signif(topR,2), ""))), 
                  color = "white", size = 2) +
        geom_text(aes(label = ifelse(is.na(topR), "", 
                                     ifelse(topR <= 1, signif(topR,2), ""))), 
                  color = "black", size = 2)+
        scale_fill_gradientn("Fold Change\n(log2)",
                             colors = c("darkblue","white","darkred"), 
                             limits = c(-0.5, topRange), 
                             values = scales::rescale(c(-0.5, 0, topRange))) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        facet_grid( ~ casestudy + cov, scales = "free", space = "free") +
        ggtitle("Impact of informative covariate on number of rejections") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.99, 0.95), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7, angle=45, margin = margin(t=0)),
              legend.title = element_text(size = 9, margin=margin(t=-10)),
              legend.margin = margin(t=2, r=10, b=-2, l=10))

Fig_impactofinfcov_fc
ggsave(file.path(outdir, "Figure_impactofinfcov_fc.pdf"), width = 15.5, height = 4.25)

@@

dftab <- left_join(dftab, maxVals, by = c("casestudy")) %>%
  dplyr::mutate(top = ifelse(diff_inf_percent == top, diff_inf_percent, NA)) %>%
  dplyr::mutate(topR = ifelse(diff_inf_ratio == topR, diff_inf_ratio, NA)) %>%
  ungroup() %>%
  dplyr::mutate(casestudy = factor(casestudy, levels = colOrder)) %>%
  dplyr::mutate(casestudyN = paste0(casestudy, "(", maxd, ")")) %>%
  dplyr::mutate(casestudyN = factor(casestudyN, 
                             levels = unique(casestudyN)[unique(as.numeric(casestudy))]))

@@

Fig_impactofinfcov_fc <- ggplot(dftab, aes(x = casestudy, y = method, fill = diff_inf_ratio)) + 
        geom_tile() + 
        scale_fill_gradientn("Fold Change\n(log2)",
                             colors = c("darkblue","white","darkred"), 
                             limits = c(-0.5, topRange), 
                             values = scales::rescale(c(-0.5, 0, topRange))) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        ggtitle("Impact of informative covariate") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
        geom_text(aes(label = ifelse(is.na(topR), "", #adaptive text lab color
                                     ifelse(topR > 1, signif(topR, 2), ""))), 
                  color = "white", size = 2) +
        geom_text(aes(label = ifelse(is.na(topR), "", 
                                     ifelse(topR <= 1, signif(topR, 2), ""))), 
                  color = "black", size = 2)  +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.945, 0.94), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7, angle=45, margin = margin(t=2)),
              legend.title = element_text(size = 9, margin=margin(t=-10)),
              legend.margin = margin(t=2, r=10, b=-6, l=10))

Fig_impactofinfcov_fc
ggsave(file.path(outdir, "Figure_impactofinfcov_avg_fc.pdf"), width = 5, height = 4)

@@

pfdr <- ggplot(dftab, aes(x = size, y = method, fill = fdr_diff)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(top_fdr), "",  scales::percent(top_fdr))), 
                  color = "black", size = 2) +
        scale_fill_gradientn("Absolute\nFDR change",
                             labels = scales::percent, 
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.01,0,.01)),
                             guide = "colorbar", oob=scales::squish,
                             limits=c(-.01,0.01)) +
        xlab("") + ylab("") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1))

ptpr <- ggplot(dftab, aes(x = size, y = method, fill = tpr_diff)) + 
        geom_tile() + 
        geom_text(aes(label = ifelse(is.na(top_tpr), "",  scales::percent(top_tpr))), 
                  color = "black", size = 2) +
        scale_fill_gradientn("Absolute\nTPR change",
                             labels = scales::percent, 
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.01,0,.1)),
                             guide = "colorbar", oob=scales::squish,
                             limits=c(-.01,0.1)) +
        xlab("") + ylab("") +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1))

@@

ggdraw() +
  draw_plot(pfdr, 0.53, 0.025, 0.24, 0.93) +
  draw_plot(ptpr, 0.77, 0.025, 0.24, 0.93) +
  draw_plot(Fig_impactofinfcov_fc, 0, 0, 0.52, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.53), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.71, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure_impactofinfcov_avg_sim_fc.pdf"), width=9.5, height=5)
